{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-30 paper/tex/sections/appendix.tex
fix equation b6 description

\textit{Common Envelope:} A common-envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}. We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope. For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}. We assume that any Hertzsprung gap donor stars that initiate a common-envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}. This follows the `pessimistic' common-envelope scenario \citep[c.f.][]{Belczynski+2007}. We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common-envelope phase as we treat these as failed common-envelope ejections, likely leading to a stellar merger.

@@

The total star forming mass at a metallicity $Z$, $M_{\rm SF, Z}$, can be written as
\begin{equation}
    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
\end{equation}
where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}). These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from.

>>>>

\textit{Common-Envelope:} A common-envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}. We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope. For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}. We assume that any Hertzsprung gap donor stars that initiate a common-envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}. This follows the `pessimistic' common-envelope scenario \citep[c.f.][]{Belczynski+2007}. We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common-envelope phase as we treat these as failed common-envelope ejections, likely leading to a stellar merger.

@@

The total star forming mass at a metallicity $Z$, $M_{\rm SF, Z}$, can be written as
\begin{equation}
    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} N_{\rm binaries, Z},
\end{equation}
where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in a simulation using our cutoffs (discussed in Section~\ref{sec:COMPAS_explained}) and $f_{\rm trunc}$ is the fraction of the total stellar mass from which our COMPAS simulations sample, given our truncated mass and separation ranges (see Section~\ref{sec:COMPAS_explained}). These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from.
